Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-03-15 Paper/RSVOptimization.rnw
Todo re citing spatial variability
Missing author list line break
Revised previous research on spatial variability

\author{
    \authorstyle{Ben Artin, MEng, MPH, MMSc\textsuperscript{1}}
    \authorstyle{Daniel Weinberger, PhD\textsuperscript{1}}\\
    \authorstyle{Virginia Pitzer, ScD\textsuperscript{1}}
    \newline\newline
    \textsuperscript{1}\institution{Yale University, School of Public Health}
}

@@

RSV seasonality and spatial variability have been established throughout the United States, based on National Respiratory and Enteric Virus Surveillance System data. In all states except for Florida, RSV shows an annual or biennial cycle with a stable seasonal onset between mid-November and early January and a stable seasonal offset between mid-March and late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv} RSV season in Florida begins approximately two months earlier than in other states. \cite{CentersforDiseaseControlandPreventionCDC:2013wv} The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida --- does not recommend local variance from nationwide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}

Previous analysis of RSV-associated hospital admissions in Connecticu has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188} No prior research is available regarding year-to-year variation in timing of RSV season in Connecticut.

>>>>

\author{
    \authorstyle{Ben Artin, MEng, MPH, MMSc\textsuperscript{1}}\\
    \authorstyle{Daniel Weinberger, PhD\textsuperscript{1}}\\
    \authorstyle{Virginia Pitzer, ScD\textsuperscript{1}}
    \newline\newline
    \textsuperscript{1}\institution{Yale University, School of Public Health}
}

@@

% TODO cite DW/VP paper re spatial variability

RSV seasonality and spatial variability have been established throughout the United States, based on National Respiratory and Enteric Virus Surveillance System data; RSV has been found to have an annual or biennial cycle with regionally variable seasonal onset ranging from late August to mid-December and offset ranging from mid-March to late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv,Weinberger:2015hj} The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida, whose RSV season leads most of the rest of the nation by approximately two months --- does not recommend local variance from nationwide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}

Previous analysis of RSV-associated hospital admissions has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188} No prior research is available regarding year-to-year variation in timing of RSV season in Connecticut.
